Response to reviewers

### 2013-02-27 response.tex

Thank you for the careful reading of our manuscript and the referee
report and we deeply appreciate your comments and critiques on the
manuscript. The specific comments and suggestions for review have been
followed, and the result is an improved manuscript. In particular,
the discussions surrounding the theoretical results in Section IV and
the experiments in Section V had been expanded, most importantly the
addition of Figure 5, illustrating, through Q-Q plots, 
the convergence of the statistics to their limiting distribution. Below we
give specific responses to the comments of the reviewers.  Again, we
thank the editor and reviewers for their valuable comments.

### 2013-02-27 response2.tex
Version accepted to TSP

Thank you for the careful reading of our manuscript and the referee
report and we deeply appreciate your comments and critiques on the
manuscript. The specific comments and suggestions for review have been
followed, and the result is an improved manuscript. In particular,
the discussions surrounding the theoretical results in Section IV and
the experiments in Section V had been expanded, most importantly the
addition of Figure 5, illustrating, through Q-Q plots, 
the convergence of the statistics to their limiting distribution. Below we
give specific responses to the comments of the reviewers.  Again, we
thank the editor and reviewers for their valuable comments.

==================================================
Reviewer: 1

Recommendation: AQ - Publish In Minor, Required Changes

Comments:
(1) Expand the discussion on the connection of your approach with the
wavelet representations for graphs; a small paragraph, 3-4 sentences,
would suffice.

*** Response: 
We have expanded the discussion on related works. In
particular, we described the similarities between the construction and
use of the wavelet representation for traffic analysis in [Crovella & Kolaczyk, 2003] and
anomaly detection using locality/scan statistics in our manuscript.

(2) Comment more explicitly on the choice of the running-average window l. Is there a guideline?

@@

(3) Add reference [*] [*] C. E. Priebe, N. H. Lee, Y. Park, and
M. Tang, "Attribute Fusion in a Latent Process Model for Time Series
of Graphs," 2011 IEEE Workshop on Statistical Signal Processing
(SSP2011), July 2011.
*** Response: This had been done.

==================================
Reviewer: 2

@@

(1) The paper has been improved somewhat but it is still written in a
terse mathematical style that is not consistent with the signal
processing audience. The introductory section is from [1] but the
reader would not know this if [1] had not been read.  The Lemmas and
Theorems in the power analysis section are inadequately discussed in
terms of their practical applicability to problems of signal
processing and time series analysis. In particular, the weak
convergence theory of Thms 4, 6 and 9 is interesting but the utility
of these theorems is not adequately illustrated.  The Gumbel limits
are not explained, interpreted or illustrated in the numerical
section. The authors could, for example, illustrate how these results
can be used to set thresholds or select the linear parameter
lambda. How large does n and l have to be for these limits to become
good apprxoimation? Q-Q plots of simulation or real (Enron) data
against student-t and Gumbel would give an idea of how fast these
approximations converge.  In any case, any theoretical results that
are not illustrated for a SP problem should be removed from the paper.

*** Response 
We have reorganized and expanded the paper to make the connections
between the theoretical results in Section IV and their applicability
to signal processing and time-series analysis more explicit. In
particular, section IV now starts off with a discussion relating the
change-point detection framework in Section III with the theoretical
results, i.e., the theoretical results provided power estimates for
each choice of the fusion parameter $\lambda$. We have also note how
the theoretical results in this paper are extensions of results that 
exist in the literature.

@@

***

(2) The Introduction should very clearly state the differences between [1]
and the present work. The reader should not have to read [1], which
this reviewer did, in order to figure this out.

*** Response
The manuscript now include a short paragraph at the end of the introductory
section describing the relationships between [1], another paper that
was an earlier version of the manuscript and was presented at the 2011
SSP workshop in Nice, France, and the manuscript. In particular the
current manuscript used the generative model for the time-series of graphs
from [1]. Also, the setup of anomaly/change-point detection and the
use of temporal standardization of the graph invariants as the test
statistics are also identical to that done in [1] (this setup or
its variation had been used previously by some of the authors, see
e.g., Priebe et al ``Scan statistics on Enron graphs''). However, [1] only
considered the use of the size invariant. The earlier version of the
manuscript that was presented at the 2011 SSP workshop motivates the
current manuscript and include a preliminary version of the simulation
experiment in Section V.  
***

(3) In Fig 4 the 1st and 2nd order approximations appear to upper bound
the exact curve for all cases studied.  Is this provable? The authors
should comment.

*** Response
Two of the authors of the manuscript had noticed the above
phenomenon (and the fact that the 2nd-order approximation is monotone
increasing in $r$, the process rate parameter) in their previous paper
[1]. However, they have not been able to explain the phenomenon. It
might be possible to show that the
second-order approximations is monotone increasing in $r$, which also implies
that the first-order approximation is an upper bound for the second order
approximations, for the size and number of triangle statistic using some
recent results in [2]. However, to the best of our knowledge,
the explanation for the full phenomenon is still elusive. We would be
very much interested in knowing an explanation behind this phenomenon.

@@

(4) Non-standard notation (e.g. [n], [K+1]) has now been defined but
it should be aligned with a more standard notation (e.g. {1,...,n} and
{1,...,K+1}) familar to SP audience. There are also many typographical
errors in the manuscript. The authors need to go through and carefully
correct errors of syntax and omissions of important assumptions. A
sampling of the ones I found is:

* Eqn (2) , <x_u,x_v> should be <X_u,X_v>.
*Line 14 on p. 5: "phenoma" should be "phenomenon"
*Line 19 on p. 5; "Permutation of the vertex labels does not affect
our subsequent analysis"
*Line 23 p 5: "Of general interests" should be replaced by "Of general interest"
*Line 31 on p 7: "parameters" should be "parameter"
*Line 4 on p 8: "interests" should be "interest"
*Line 12 on p 8: the "I" notation used to define \Gamma_{uv}(k) shoudl
be defined explicitly as a vector of indicator functions since this is
not standard notation. Furthermore, on the next line the statement
\Gamma_{uv}=0 is confusing since \Gamma_{uv} is a vector. A better
notation will be \Gamma_{uv} =[0,\ldots,0]^T.
*Thm 1 needs to be stated more precisely with all necessary
assumptions, as in [1]. The quantites defined are functions of m,n,l
and involve matrices eta_{ij}. In [1] these matrices are assumed to be
positive definite and the matrix \zeta is assumed to be
non-zero. These assumptions need to be stated here too.

*** Response
The above errors had all been fixed. In particular the statement of
the theoretical results had been revised or corrected. An additional
assumption regarding the matrix \zeta being positive definite is now
included in Theorem 1. All occurrences of the fraction $\sqrt{\pi}/6$ in Theorem 6 and
Theorem 9 had now been changed/corrected to $\sqrt{6}/pi$.

>>>>

\documentclass{article}
\pdfminorversion=4
\usepackage{parskip}
\usepackage{fontenc}
\begin{document}
\title{Response to reviewers}
\maketitle
\date{}
Thank you for the careful reading of our manuscript and the referee
report and we deeply appreciate your comments and critiques on the
manuscript. The specific comments and suggestions for review have been
followed, and the result is an improved manuscript. In particular,
the discussions surrounding the theoretical results in Section IV and
the experiments in Section V had been expanded, most importantly the
addition of Figure 5, illustrating, through Q-Q plots, 
the convergence of the statistics to their limiting distribution. Below we
give specific responses to the comments of the reviewers (the
reviewers comments are in italic). Again, we
thank the editor and reviewers for their valuable comments.

\section{Comments from Reviewer 1}
Recommendation: AQ - Publish In Minor, Required Changes

Comments:
{\em (1) Expand the discussion on the connection of your approach with the
wavelet representations for graphs; a small paragraph, 3-4 sentences,
would suffice.}

*** Response: We have expanded the discussion on related works. In
particular, we described the similarities between the construction and
use of the wavelet representation for traffic analysis in [Crovella \&
Kolaczyk, 2003] and anomaly detection using locality/scan statistics
in our manuscript.

{\em (2) Comment more explicitly on the choice of the running-average
window l. Is there a guideline?}

@@

{\em (3) Add reference [*] C. E. Priebe, N. H. Lee, Y. Park, and
M. Tang, "Attribute Fusion in a Latent Process Model for Time Series
of Graphs," 2011 IEEE Workshop on Statistical Signal Processing
(SSP2011), July 2011.}

*** Response: This had been done.

\section{Comments from Reviewer 2}

@@

{\em (1) The paper has been improved somewhat but it is still written in a
terse mathematical style that is not consistent with the signal
processing audience. The introductory section is from [1] but the
reader would not know this if [1] had not been read.  The Lemmas and
Theorems in the power analysis section are inadequately discussed in
terms of their practical applicability to problems of signal
processing and time series analysis. In particular, the weak
convergence theory of Thms 4, 6 and 9 is interesting but the utility
of these theorems is not adequately illustrated.  The Gumbel limits
are not explained, interpreted or illustrated in the numerical
section. The authors could, for example, illustrate how these results
can be used to set thresholds or select the linear parameter
lambda. How large does n and l have to be for these limits to become
good apprxoimation? Q-Q plots of simulation or real (Enron) data
against student-t and Gumbel would give an idea of how fast these
approximations converge.  In any case, any theoretical results that
are not illustrated for a SP problem should be removed from the paper.}

*** Response: We have reorganized and expanded the paper to make the
connections between the theoretical results in Section IV and their
applicability to signal processing and time-series analysis more
explicit. In particular, section IV now starts off with a discussion
relating the change-point detection framework in Section III with the
theoretical results, i.e., the theoretical results provided power
estimates for each choice of the fusion parameter $\lambda$. We have
also note how the theoretical results in this paper are extensions of
results that exist in the literature.

@@

{\em (2) The Introduction should very clearly state the differences between [1]
and the present work. The reader should not have to read [1], which
this reviewer did, in order to figure this out.}

*** Response: The manuscript now include a short paragraph at the end
of the introductory section describing the relationships between [1],
another paper that was an earlier version of the manuscript and was
presented at the 2011 SSP workshop in Nice, France, and the
manuscript. In particular the current manuscript used the generative
model for the time-series of graphs from [1]. Also, the setup of
anomaly/change-point detection and the use of temporal standardization
of the graph invariants as the test statistics are also identical to
that done in [1] (this setup or its variation had been used previously
by some of the authors, see e.g., Priebe et al ``Scan statistics on
Enron graphs''). However, [1] only considered the use of the size
invariant. The earlier version of the manuscript that was presented at
the 2011 SSP workshop motivates the current manuscript and include a
preliminary version of the simulation experiment in Section V.  ***

{\em (3) In Fig 4 the 1st and 2nd order approximations appear to upper bound
the exact curve for all cases studied.  Is this provable? The authors
should comment.}

*** Response: Two of the authors of the manuscript had noticed the
above phenomenon (and the fact that the 2nd-order approximation is
monotone increasing in $r$, the process rate parameter) in their
previous paper [1]. However, they have not been able to explain the
phenomenon. It might be possible to show that the second-order
approximations is monotone increasing in $r$, which also implies that
the first-order approximation is an upper bound for the second order
approximations, for the size and number of triangle statistic using
some recent results in [2]. However, to the best of our knowledge, the
explanation for the full phenomenon is still elusive. We would be very
much interested in knowing an explanation behind this phenomenon.

@@

{\em (4) Non-standard notation (e.g. [n], [K+1]) has now been defined but
it should be aligned with a more standard notation (e.g. {1,...,n} and
{1,...,K+1}) familar to SP audience. There are also many typographical
errors in the manuscript. The authors need to go through and carefully
correct errors of syntax and omissions of important assumptions. A
sampling of the ones I found is:

\begin{enumerate}
  \item Eqn (2) , $<x_u,x_v>$ should be $<X_u,X_v>$.
  \item Line 14 on p. 5: "phenoma" should be "phenomenon"
  \item Line 19 on p. 5; "Permutation of the vertex labels does not affect
our subsequent analysis"
\item Line 23 p 5: "Of general interests" should be replaced by "Of general interest"
\item Line 31 on p 7: "parameters" should be "parameter"
\item Line 4 on p 8: "interests" should be "interest"
\item Line 12 on p 8: the "I" notation used to define $\Gamma_{uv}(k)$ should
be defined explicitly as a vector of indicator functions since this is
not standard notation. Furthermore, on the next line the statement
$\Gamma_{uv}=0$ is confusing since $\Gamma_{uv}$ is a vector. A better
notation will be $\Gamma_{uv} =[0,\ldots,0]^T$.
\item Thm 1 needs to be stated more precisely with all necessary
assumptions, as in [1]. The quantites defined are functions of m,n,l
and involve matrices $eta_{ij}$. In [1] these matrices are assumed to be
positive definite and the matrix $\zeta$ is assumed to be
non-zero. These assumptions need to be stated here too.
\end{enumerate}}

*** Response: The above errors had all been fixed. In particular the
statement of the theoretical results had been revised or corrected. An
additional assumption regarding the matrix $\zeta$ being positive
definite is now included in Theorem 1. All occurrences of the fraction
$\sqrt{\pi}/6$ in Theorem 6 and Theorem 9 had now been
changed/corrected to $\sqrt{6}/pi$.
\end{document}

### 2013-02-27 response3.tex
Version accepted to TSP

Paper:T-SP-14347-2012, "Attribute fusion in a latent process model for
time series of graphs"

Dear Prof.  Priebe,

I am writing to you concerning the above referenced manuscript, which
you submitted to the IEEE Transactions on Signal Processing.

Based on the enclosed set of reviews (**See note below about
attachments), I have decided that the manuscript be REVISED AND
RESUBMITTED (RQ). Judging by the recommendations (RQ and A), one may
have impression that the reviewers differ in their opinions
substantially. As a matter of fact they don't. They both are very much
concerned by the fact that your paper still lacks the focus on
applicability and practicality (Reviewer #2 points this out very
strongly in the confidential part of his review). Reviewer #1 proposed
changes that could make your paper more practically oriented, and
hence more interesting for the signal processing community. I strongly
recommend that you follow his advice. This could result in a good
paper and would prevent us from wasting your efforts (which are very
much appreciated) and the efforts of the reviewers.

Your revised manuscript must be submitted back to Manuscript Central
http://mc.manuscriptcentral.com/tsp-ieee no later than 6 weeks from
the date of this letter together with a point-by-point reply that
explains how you addressed the reviewers' comments.

Please note that the reviewers will review your revised article only
one more time. The only decisions available to an AE after a second
round of reviews are A(Accepted), AQ(Accepted with Mandatory
Revisions), and R(Reject).

If we do not receive your revised manuscript within 6 weeks from the
date of this letter, your manuscript will be considered withdrawn.

To revise your manuscript, log into
http://mc.manuscriptcentral.com/tsp-ieee and enter your Author Center,
where you will find your manuscript title listed under "Manuscripts
with Decisions."  Under "Actions," click on "Create a Revision."  Your
manuscript number has been appended to denote a revision.

You will be unable to make your revisions on the originally submitted
version of the manuscript.  Instead, revise your manuscript using a
word processing program and save it on your computer.

Once the revised manuscript is prepared, you can upload it and submit
it through your Author Center.

When submitting your revised manuscript, you will be able to respond
to the comments made by the reviewer(s) in the space provided.  You
can use this space to document any changes you make to the original
manuscript.  In order to expedite the processing of the revised
manuscript, please be as specific as possible in your response to the
reviewer(s).

IMPORTANT: Your original files are available to you when you upload
your revised manuscript.  Please delete any redundant files before
completing the submission.

If you have any questions regarding the reviews, please contact me.
Any other inquiries should be directed to Rebecca Wollman.
Additionally, please provide a detailed explanation how the revised
manuscript addresses each of the comments from the reviewers.

Best regards,

Prof. Maciej Niedzwiecki
Associate Editor
IEEE Transactions on Signal Processing
maciekn@eti.pg.gda.pl, maciekn@pg.gda.pl

Rebecca Wollman
Coordinator Society Publications
IEEE Signal Processing Society
r.wollman@ieee.org

** {This applies to SUBMITTING AUTHOR Accounts ONLY: You can find any
  possible ATTACHMENTS FROM THE REVIEWERS by going to the "Manuscript
  with Decisions" status link in your Author Center and clicking on
  "view decision letter". They are located at the bottom of decision
  letter under "Files attached" heading}

Reviewer Comments:

Reviewer: 1

Recommendation: RQ - Review Again After Major Changes

Comments: The revision is much improved. The authors have included
better motivation of their approach, related the approach to signal
processing applications, included results on convergence analysis, and
reported diagnostic goodness of fit tests validating some of the
theoretical predictions.

This reviewer especially appreciates the inclusion of a review of the
weak convergence results that can be applied to specify asymptotic
distributions of the proposed test statistics.  These results are used
to compute power approximations that are in turn used to select
optimal parameters, e.g. lambda.  However, especially for a paper
emphasizing testing and anomaly detection, the principal utility of
these results are to specification of approximate p-values. Yet, the
authors do not take advantage of the stated theory on asymptotic
distributions to provide such p-values to quantify Type I error
control on statements that are made about possible anomalies- e.g. in
Figs. 7 and 8. Given the asymptotic results provided, this does not
seem difficult to do and the reviewer is somewhat puzzled that the
authors did not do it. Without such illustration of the theory, the
utility of the convergence analysis will likely be lost on the reader
and the author's final sentence "...these statistics can serve as the
basis for simple and robust inference procedures on time-series of
(attributed) graphs." suffers loss in credibility. Thus the authors
need to address this point in a next round of review.

This reviewer still found some typographical and stylistic errors in
the revision. I suggest the last author give the paper a thorough
proofread next time to improve the english syntax.  Here are some that
I found:

@@

Caption of Fig. 8: "each graph invariants" -> "each graph invariant"

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: Yes

2. Is the topic important to colleagues working in the field?: Yes

Explain:

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes

3. How would you describe technical depth of paper?: Appropriate for
the Generally Knowledgeable Individual Working in the Field or a
Related Field

4. How would you rate the technical novelty of the paper?: Somewhat Novel

1. How would you rate the overall organization of the paper?: Satisfactory

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the
length of the paper should be amended, including a possible target
length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: Yes

5. How do you rate the English usage? : Needs improvement

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Good

2. How would you rate the novelty of the paper?: Sufficiently Novel

3. How would you rate the "literary" presentation of the paper?: Mostly Accessible

4. How would you rate the appropriateness of this paper for
publication in this IEEE Transactions?: Good Match

Reviewer: 2

Recommendation: A - Publish Unaltered

Comments: 
The authors improve their previous version of the manuscript
by introducing incremental changes including the following:

1. An expansion of the literature on corresponding wavelet
representations and the connection of this manuscript to previous
works (citations [1] and [7]) in Section 1.

2. A comment on the choice of the value of l and a minor section
restructuring (at the boundaries of Section 3 and 4).

3. Q-Q plots and a small discussion on relating the theoretical
results to their first simulation example (mainly second paragraph of
Section 5).

4. Potential benefits from generalizations of their results (the last
two paragraphs of Section 6).

Very minor typos: i) the size of a n-hop neighborhood -> the size of
an n-hop neighborhood (page 2, line 48) ii) all the n-hop neighborhood
-> all n-hop neighborhoods (page 2, line 52)

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: Perhaps

2. Is the topic important to colleagues working in the field?: Moderately So

Explain:

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes

3. How would you describe technical depth of paper?: Appropriate for
the Generally Knowledgeable Individual Working in the Field or a
Related Field

4. How would you rate the technical novelty of the paper?: Not Novel

1. How would you rate the overall organization of the paper?: Satisfactory

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the
length of the paper should be amended, including a possible target
length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: Yes

5. How do you rate the English usage? : Satisfactory

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Good

2. How would you rate the novelty of the paper?: Not Novel

3. How would you rate the "literary" presentation of the paper?: Mostly Accessible

4. How would you rate the appropriateness of this paper for
publication in this IEEE Transactions?: Weak Match
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass{article}
\pdfminorversion=4
\usepackage{parskip}
\usepackage{fontenc}
\begin{document}
\title{Response to reviewers}
\maketitle
\date{} Thank you for the careful re-reading of our manuscript and the
referee report and we deeply appreciate your comments and critiques on
the manuscript. The specific comments and suggestions for review have
been followed. The
comments on the lack of p-values are particularly relevant and we thank
the referees for pointing it out once again. We went back to the 
experiments on the Enron email corpus to obtain p-values for using
$T_{\lambda}^{l}$ as a statistic for hypothesis testing. The results
are detailed in Section 5 (on pages 9 \& 10 of the double column
version of the manuscript). Below we
give specific responses to the comments of the reviewers (the
reviewers comments are in italic). 
\section{Comments from Reviewer 1}
Recommendation: RQ - Review Again After Major Changes

Comments: 
{\em (1) The revision is much improved. The authors have included
better motivation of their approach, related the approach to signal
processing applications, included results on convergence analysis, and
reported diagnostic goodness of fit tests validating some of the
theoretical predictions.

This reviewer especially appreciates the inclusion of a review of the
weak convergence results that can be applied to specify asymptotic
distributions of the proposed test statistics.  These results are used
to compute power approximations that are in turn used to select
optimal parameters, e.g. lambda.  However, especially for a paper
emphasizing testing and anomaly detection, the principal utility of
these results are to specification of approximate p-values. Yet, the
authors do not take advantage of the stated theory on asymptotic
distributions to provide such p-values to quantify Type I error
control on statements that are made about possible anomalies- e.g. in
Figs. 7 and 8. Given the asymptotic results provided, this does not
seem difficult to do and the reviewer is somewhat puzzled that the
authors did not do it. Without such illustration of the theory, the
utility of the convergence analysis will likely be lost on the reader
and the author's final sentence "...these statistics can serve as the
basis for simple and robust inference procedures on time-series of
(attributed) graphs." suffers loss in credibility. Thus the authors
need to address this point in a next round of review.
}

*** Response: The p-values for the Enron email corpus were something we
should have done in earlier versions of the manuscript and we agree
with the referee that the principal utility of the theoretical results
in Section IV is to the specification of these approximate
p-values. We believe that the discussion on p-values in this new
version is a succinct example of the utility of the theoretical results.

{\em (2): This reviewer still found some typographical and stylistic errors in
the revision. I suggest the last author give the paper a thorough
proofread next time to improve the english syntax.  Here are some that
I found:

@@

Caption of Fig. 8: "each graph invariants" -> "each graph invariant"
}

*** Response*** 
We have gone through the manuscript to check for errors in grammatical usage.

\section{Comments from Reviewer 2}
Recommendation: A - Publish Unaltered

Comments: 
{\em The authors improve their previous version of the manuscript
by introducing incremental changes including the following:

Very minor typos: i) the size of a n-hop neighborhood -> the size of
an n-hop neighborhood (page 2, line 48) ii) all the n-hop neighborhood
-> all n-hop neighborhoods (page 2, line 52)}

*** Response ***
We have fixed these and other typos noted by the first referee in the text.
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% End:
